Measuring Individual Partisan Harm in Redistricting

### 2021-09-07 paper/paper.Rmd
comment out temp figure

Harm is defined using the local, not global, utility measure, because inherently, global utility (and thus harm) will be constant for all voters of a particular party.
In fact, a harm measure defined analogously using global utility would essentially be a difference in seats won by a voter's party between plans $q$ and $\tilde q$ (the exact form would be affected by the function $g$).
This measure is not particularly interesting, and nor is it novel, being a standard measure of partisan harm in simulation-based redistricting litigation, up to a monotonic transformation [@2018league; @2019rucho; @2019lewis]. **[CM: revisit ¶ based on NJ findings]****.**

@@

```{r nj-vars, fig.cap="Various measures for an ensemble of New Jersey districting plans.", fig.width=6.5, fig.height=6.5}
include_graphics(here("out/nj_vars.pdf"))
```

>>>>

Harm is defined using the local, not global, utility measure, because inherently, global utility (and thus harm) will be constant for all voters of a particular party.
In fact, a harm measure defined analogously using global utility would essentially be a difference in seats won by a voter's party between plans $q$ and $\tilde q$ (the exact form would be affected by the function $g$).
This measure is not particularly interesting, and nor is it novel, being a standard measure of partisan harm in simulation-based redistricting litigation, up to a monotonic transformation [@2018league; @2019rucho; @2019lewis].
**[CM: revisit ¶ based on NJ findings].**

@@

```{r nj-vars, fig.cap="Various measures for an ensemble of New Jersey districting plans.", fig.width=6.5, fig.height=6.5}
#include_graphics(here("out/nj_vars.pdf"))
```
